Characterization of gaps in directly bonded Si compound optics

### 2014-05-01 AO_bondedSi.tex
tweaks here and there, especially to tables

% Figures (shared wavelength axis)
%	2) Fresnel transmission as a function of wavelength (normal incidence)
%	4) Example transmission through VG03 thick gap

@@

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines, Fig. \ref{figVG03pattern} \\         
    Mesh F & 50 & 40 &  100 $\mu$ square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$ square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$ square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

%\caption{Summary of X-ray CT measurements for VG03 \label{tab:tablenum4}}
\begin{center}
    \begin{tabular}{ll}
    \emph{Parameter (Units)} & \emph{Value} \\ 
    Instrument& Xradia MicroCT \\
     Objective & 0.7X \\
    Accelerating voltage (kV) & 100 \\
        Power (W) & 10 \\
        Acquisition time (s) & 3.5 \\
        Number of views & 2521 \\
        Total slices & 469 \\
        Field of view diameter (pixels) & 988 \\
        Voxel lateral pixel resolution ($\mu$m) & 38.02 \\
        Estimate field of view (mm) & 37.5 \\
        Voxel axial pixel resolution ($\mu$m) & 0.5 \\
        Scan date & 2013 August 8 \\
        Sample thickness (mm) & 6.6 \\
     \end{tabular}
\end{center}

>>>>

@@

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines, Fig. \ref{figVG03pattern} \\         
    Mesh F & 50 & 40 &  100 $\mu$m square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$m square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$m square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{table}[h!]
\caption{Summary of X-ray CT measurements for VG03 \label{tab:tablenum4}}
\begin{center}
    \begin{tabular}{ll}
    \hline
    \emph{Parameter (Units)} & \emph{Value} \\ 
    \hline
    Instrument& Xradia MicroCT \\
     Objective & 0.7X \\
    Accelerating voltage (kV) & 100 \\
        Power (W) & 10 \\
        Acquisition time (s) & 3.5 \\
        Number of views & 2521 \\
        Total slices & 469 \\
        Field of view diameter (pixels) & 988 \\
        Voxel lateral pixel resolution ($\mu$m) & 38.02 \\
        Estimate field of view (mm) & 37.5 \\
        Voxel axial pixel resolution ($\mu$m) & 0.5 \\
        Scan date & 2013 August 8 \\
        Sample thickness (mm) & 6.6 \\
    \hline
     \end{tabular}
\end{center}
\end{table}
